HO unification from object language to meta language

### 2024-04-03 paper/main.tex
corollary->lemma

% This property can be relaxed, to accept approximations: a dedicated
% section is given in a future section
\begin{corollary}
  If the \lhs of a \linkbeta is instantiated to a rigid term and its \rhs
  counterpart is still in \maybebeta,
  the original unification problem is not in \llambda
  % \noteE[inline]{non capisco cosa vuoi dire con "the current...". Data la prova sotto vuoi dire che il problem originale sarebbe stato fuori... e quindi falliamo}
  %\noteE[inline]{Is it clearer?}
  and the unification fails.
  \label{cor:keep-fidelity}
\end{corollary}

@@

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by \cref{DA FARE}, the problem 
  unifies iff its corresponding \Fo{} unifies too. If $\sigma\hoUnifPb$ is in 
  \maybebeta, then, by \cref{cor:keep-fidelity}, the unification fails, as per
  the corresponding unification in \Fo{}.
\end{proof}

>>>>

% This property can be relaxed, to accept approximations: a dedicated
% section is given in a future section
\begin{lemma}
  If the \lhs of a \linkbeta is instantiated to a rigid term and its \rhs
  counterpart is still in \maybebeta,
  the original unification problem is not in \llambda
  % \noteE[inline]{non capisco cosa vuoi dire con "the current...". Data la prova sotto vuoi dire che il problem originale sarebbe stato fuori... e quindi falliamo}
  %\noteE[inline]{Is it clearer?}
  and the unification fails.
  \label{lemma:keep-fidelity}
\end{lemma}

@@

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by \cref{DA FARE}, the problem 
  unifies iff its corresponding \Fo{} unifies too. If $\sigma\hoUnifPb$ is in 
  \maybebeta, then, by \cref{lemma:keep-fidelity}, the unification fails, as per
  the corresponding unification in \Fo{}.
\end{proof}
